Empowering Multi-Span Question Answering with Expansive Information Injection using Large Language Models

### 2023-09-09 paper.tex
Add files via upload

\usepackage{color}
\usepackage[utf8]{inputenc}
\usepackage{xeCJK}
\setCJKmainfont{STKaiti}

@@

\begin{figure}[H]
	\includegraphics[width=14.0cm]{overview}
	\caption{An overview of our automatic information augmentation framework. \textbf{(a) Step 1}: Interact with ChatGPT to Get Auxiliary Information. \textbf{(b) Step 2}: Distilling the Information and Injecting Them into Context \textbf{(c) Step 3}: Input the Augmented Context into Tagging Model}
	\label{fig:overview}
\end{figure}   
\unskip

@@

\begin{table}[H] 
	\caption{The constructed Chinese QA corpus in automotive domain.} \label{tab:base_corpus}
	\newcolumntype{C}{>{\centering\arraybackslash}X}
	\begin{tabularx}{\textwidth}{C}
		\toprule
		\textbf{An Example of QA pairs}	\\
		\midrule
		\{ ``id'': 0,~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \\
		``question'': ``WEY是什么品牌的车?'',~~~~~~~~~~~~~~~~~~~~~~ \\
		~~~~~~~~~~ ({\color{blue} Which automobile brand is WEY?}) \\ 
		``answer'': ``WEY是长城汽车旗下的高端品牌…'', ~~~~~~~\\
		 ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~({\color{blue} WEY is a high-end brand under Great Wall Motors…}) \\
		\}~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\\
%		\midrule
%		Entry 1		\\
%		Entry 2	Dat \textsuperscript{1}\\
		\bottomrule
	\end{tabularx}
%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
\end{table}

\begin{table}[H] 
	\caption{The constructed Chinese QA corpus in automotive domain.} \label{tab:annotated_corpus}
	\newcolumntype{C}{>{\centering\arraybackslash}X}
	\begin{tabularx}{\textwidth}{p{2cm}L} 
		\toprule
		\textbf{Name}  & \textbf{Data Format}	\\
		\midrule
		MLM Corpus  & \textbf{[MASK][MASK]}车队首次在1994年的JGTC第四站比\textbf{[MASK]}中亮相，获得了资格赛第二名的位置。{\color{blue} (The [MASK] team made its debut in the fourth round of the JGTC  in 1994, securing the second position in the qualifying [MASK].) } \\
		\midrule
		NSP Corpus  & \textbf{Sentence1}: 上世纪90年代，TRD为丰田TOM'S车队打造了Supra赛车。{\color{blue} (In the 1990s, TRD built Supra race cars for the Toyota TOM'S team.) }
		\textbf{Sentence2}: 丰田车队首次在1994年的JGTC第四站比赛中亮相，获得了资格赛第二名的位置。{\color{blue} (The Toyota team made its debut in the fourth round of the JGTC  in 1994, securing the second position in the qualifying race.)} ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\textbf{Label}: continuous (1)\\
		\midrule
		STS Corpus & \textbf{Sentence1}: 丰田车队首次在1994年的JGTC第四站比赛中亮相，获得了资格赛第二名的位置。{\color{blue} (The Toyota team made its debut in the fourth round of the JGTC  in 1994, securing the second position in the qualifying race.)}
		\textbf{Sentence2}: 在1994年的JGTC第四站比赛中，丰田车队首次参赛，并在资格赛中获得了第二名的成绩。{\color{blue} (In 1994, during the fourth round of the JGTC, the Toyota team made its debut and secured a second-place finish in the qualifying race.)} ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \textbf{Label}: similar (1) ~~~~~~~~		\\
		\midrule
		TE Corpus  &  \textbf{Sentence1}: 一个年轻的黑人正试图向另外两个人解释一些事情。{\color{blue} (A young black person is trying to explain something to two other individuals.)}
		\textbf{Sentence2}: 一位年轻的黑人男子正在和另外两位说话。{\color{blue} (A young black man is talking to two other people.)} ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \textbf{Label}: entailment (0) ~~~~~		\\
		\bottomrule
	\end{tabularx}
	%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
\end{table}

@@

\subsection{Experimental Results and Analysis}
	In this section, we compare $\text{AUG}$ with all competing models described above \textcolor{red}{both quantitatively and qualitatively}.

@@

	\begin{table}[H] 
		\caption{Approach performance on complete MultiSpanQA valid set based on $\text{RoBERTa}_{base}$.} 
		\label{tab:robertaall}
		\newcolumntype{C}{>{\centering\arraybackslash}X}
		\begin{tabularx}{\textwidth}{p{1.5cm}CCCCCCC}
			\toprule
			\multirow{2}{*}{\textbf{Model}} & \multicolumn{3}{c}{Exact Match} & \multicolumn{3}{c}{Partial Match}  \\
			\cline{2-7} 
			\addlinespace
			& F\((\%)\) & P\((\%)\) & R\((\%)\) & F\((\%)\) & P\((\%)\) & R\((\%)\) \\
			\midrule
			TASE & 68.00 & 65.06 & 71.22 & 83.13 & 83.05 & 83.22 \\ 
			LIQUID & 68.33 & 66.68 & 70.07 & 82.71 & 82.45 & 82.98 \\
			$\text{AUG}_{c}$ & 70.35 & 67.35 & 73.63 & 84.06 & 83.38 & 84.76 \\
			$\text{AUG}_{eree}$ & 69.15 & 67.81 & 70.54 & 82.85 & 83.90 & 81.83 \\
			$\text{AUG}_{ereec}$ & 70.44 & 67.813 & 73.26 & 82.80 & 82.45 & 83.15 \\
			Bagging & 70.86 & 69.03 & 72.79 & 84.82 & 85.53 & 84.12 \\
			\bottomrule
		\end{tabularx}      
		%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
	\end{table}
	Table~\ref{tab:bertall} and Table~\ref{tab:robertaall} illustrate the performance comparison between the proposed approaches, $\text{AUG}_{c}$ and $\text{AUG}_{eree}$, and several strong baselines, including the previous state-of-the-art model LIQUID. These comparisons are conducted using both the $\text{BERT}_{base}$ and $\text{RoBERTa}_{base}$ encoders, and regard multi-span question answering as a \textit{BIO} sequence tagging task to predict each token whether it is a part or begin of an answer. 
	Notably,$\text{AUG}_{c}$ exhibit superior performance across the evaluate dataset on all metrics. However, on Partial Match scores, $\text{AUG}_{eree}$ demonstrates slightly lower performance compared to TASE, and especially lower than LIQUID when employing the $\text{BERT}_{base}$ encoder.
	Importantly, the performance of $\text{AUG}_{c}$ consistently outperforms LIQUID and TASE on all metrics and encoders, irrespective of the encoder setting.
	These results demonstrate the effectiveness of our proposed framework, as well as the efficacy of the information augmentation strategy.

@@

\subsubsection{\textit{Discussion}}

@@

>>>>

\usepackage{color}
\usepackage[utf8]{inputenc}
\usepackage{xeCJK}

@@

\begin{figure}[H]
	\includegraphics[width=14.0cm]{overview}
	\caption{An overview of our automatic information augmentation framework. \textbf{(a) Step 1}: Interact with ChatGPT to Get Auxiliary Information. \textbf{(b) Step 2}: Distilling the Information and Injecting Them into Context \textbf{(c) Step 3}: Input the Augmented Context into Tagging Model}
	\label{fig:overview}
\end{figure}   
%\unskip

@@

@@

\subsection{Experimental Results and Analysis}
	In this section, we compare $\text{AUG}$ with all competing models described above quantitatively.

@@

	\begin{table}[H] 
		\caption{Approach performance on complete MultiSpanQA valid set based on $\text{RoBERTa}_{base}$.} 
		\label{tab:robertaall}
		\newcolumntype{C}{>{\centering\arraybackslash}X}
		\begin{tabularx}{\textwidth}{p{1.5cm}CCCCCCC}
			\toprule
			\multirow{2}{*}{\textbf{Model}} & \multicolumn{3}{c}{Exact Match} & \multicolumn{3}{c}{Partial Match}  \\
			\cline{2-7} 
			\addlinespace
			& F\((\%)\) & P\((\%)\) & R\((\%)\) & F\((\%)\) & P\((\%)\) & R\((\%)\) \\
			\midrule
			TASE & 68.00 & 65.06 & 71.22 & 83.13 & 83.05 & 83.22 \\ 
			LIQUID & 68.33 & 66.68 & 70.07 & 82.71 & 82.45 & 82.98 \\
			$\text{AUG}_{c}$ & 70.35 & 67.35 & 73.63 & 84.06 & 83.38 & 84.76 \\
			$\text{AUG}_{eree}$ & 69.15 & 67.81 & 70.54 & 82.85 & 83.90 & 81.83 \\
			$\text{AUG}_{ereec}$ & 70.44 & 67.83 & 73.26 & 82.80 & 82.45 & 83.15 \\
			Bagging & 70.86 & 69.03 & 72.79 & 84.82 & 85.53 & 84.12 \\
			\bottomrule
		\end{tabularx}      
		%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
	\end{table}
	Table~\ref{tab:bertall} and Table~\ref{tab:robertaall} illustrate the performance comparison between the proposed approaches, $\text{AUG}_{c}$ and $\text{AUG}_{eree}$, and several strong baselines, including the previous state-of-the-art model LIQUID. These comparisons are conducted using both the $\text{BERT}_{base}$ and $\text{RoBERTa}_{base}$ encoders, and regard multi-span question answering as a \textit{BIO} sequence tagging task to predict each token whether it is a part or begin of an answer. 
	Notably,$\text{AUG}_{c}$ exhibit superior performance across the evaluate dataset on all metrics. However, on Partial Match scores, $\text{AUG}_{eree}$ demonstrates slightly lower performance compared to TASE, and especially lower than LIQUID when employing the $\text{BERT}_{base}$ encoder.
	Importantly, the performance of $\text{AUG}_{c}$ consistently outperforms LIQUID and TASE on all metrics and encoders, irrespective of the encoder setting.
	These results demonstrate the effectiveness of our proposed framework, as well as the efficacy of the information augmentation strategy.

@@

\subsubsection{\textit{Discussion}}
	Besides, Table~\ref{tab:bertall} and Table~\ref{tab:robertaall} also discuss the performance of different augmentation integrated strategies, including the results-bagging methods whose outputs are voting results of $\text{AUG}_{c}$, $\text{AUG}_{eree}$ as well as LIQUID, and the input-fusion model $\text{AUG}_{ceree}$ who injects all kinds of information above into input contexts.

	In detail, with EM f1 scores of 62.90 and 64.44 in Table~\ref{tab:bertall} and 70.44 and 70.86 in Table~\ref{tab:robertaall}, both the $\text{AUG}_{ceree}$ and Bagging methods consistently surpass TASE and LIQUID, which exhibits robust effectiveness of information injection strategies. However, there is a little decrease caused by fusing all auxiliary information when contrast with single information augmentation strategies and the bagging method. This may be due to the likelihood that incorporating all of the augmentation information into the model inputs will confuse the model by introducing excessive auxiliary knowledge and underrepresented original context proportion. Therefore it may be more useful that adding limit information into context, and using result-bagging method, a multi-model voting to bringing all information into model with an indirect way.

	From the Partial Match perspective, $\text{AUG}_{ceree}$ and the Bagging method achieve 76.72 and 79.52 in Table~\ref{tab:bertall}, and 82.80 and 84.82 in Table~\ref{tab:robertaall}. In accordance with Exact Match metrics, Bagging demonstrate a overall superior performance. Meanwhile overlap f1 score of $\text{AUG}_{eree}$ is inferior to TASE but superior to LIQUID ,with relatively higher precision and relativelv higher recall, which  is comparable to all single augmented models such as $\text{AUG}_{eree}$. And its weak performance on overlap f1 also reveals complete entities preference of this information injection approach.

	In addition, we	categorized the data in MultispanQA into DESC, NUM, ENTYS in terms of answer types, and compared the performance of each of the model mentioned above in each breakdown category. Specifically,  Table~\ref{tab:bertsub} and Table~\ref{tab:robertasub} present the results backed by  $\text{BERT}_{base}$ and $\text{RoBERTa}_{base}$, respectively. As shown in Tables~\ref{tab:bertsub},Table~\ref{tab:robertasub}, our proposed models display superior performance in DESC and ENTYS categories answer extraction, which to some extent indicates the enhancement of models' knowledge at entity and description levels.

@@

\subsubsection{\textit{Ablation Experiment}}

\begin{table}[H] 
	\caption{$\text{AUG}_{c}$'s performance with different information injection proportion on complete MultiSpanQA valid set based on $\text{BERT}_{base}$.} 
	\label{tab:different_ratio}
	\newcolumntype{C}{>{\centering\arraybackslash}X}
	\begin{tabularx}{\textwidth}{p{1.7cm}CCCCCCC}
		\toprule
		\multirow{2}{*}{\textbf{Proportion}} & \multicolumn{3}{c}{Exact Match} & \multicolumn{3}{c}{Partial Match}  \\
		\cline{2-7} 
		\addlinespace
		& F\((\%)\) & P\((\%)\) & R\((\%)\) & F\((\%)\) & P\((\%)\) & R\((\%)\) \\
		\midrule
		0.90 & 56.60 & 54.27 & 59.13 & 71.79 & 73.90 & 71.79 \\ 
		0.70 & 56.36 & 63.11 & 63.11 & 75.87 & 77.25 & 74.54 \\
		0.50 & 57.92 & 52.82 & 64.10 & 76.82 & 76.78 & 76.86 \\
		0.40 & 58.48 & 53.99 & 63.79 & 77.35 & 77.58 & 77.13 \\
		0.10 & 53.18 & 64.48 & 77.02 & 77.02 & 77.02 & 77.02 \\
		\bottomrule
	\end{tabularx}      
	%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
\end{table}
